\documentclass[12pt]{article}
\usepackage{capt-of}
\usepackage{colortbl}
\usepackage{gensymb}
\usepackage[top=1in,left=1.5in,right=1in]{geometry}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage{float}
\usepackage{tabularx}
\usepackage{listings} 
\usepackage{ltablex}
\usepackage{hyperref}
\usepackage{tabu}
\usepackage{upgreek}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{tablefootnote}
\usepackage[nottoc,numbib]{tocbibind}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=black}
\begin{document}
\include{Title.tex}
\pagenumbering{gobble}
\tableofcontents
\listoffigures
\listoftables
\pagebreak
\pagenumbering{arabic}
%\input{your tex file here}
\section{Executive Summary}                     % Section 1
Soil characterization is shifting away from laboratory analysis and toward optical
sensing. While chemistry experiments may determine soil composition with high degrees of accuracy,
they are unfeasible on economies of scale. Every sample must be preserved for a trip back to the lab,
and lab work takes time and other valuable resources to evaluate even a single sample. Some lab work
can be done in the field, but this limits the accuracy and types of elements that can be investigated.
Spectral sensing offers two advantages: results returned by devices are limited only by scanning speeds
and computing power, and scanning covers a lot of ground, rather than a small spot. There is now a
market for precision agricultural technology, and research is ongoing to improve the efficiency of
these devices.

Soil Scanners, like those developed by AgroCares, MertControl Group, and NPC Agro, typically employ
a broadband light source to probe the soil, then collect reflectance data using an array of photodetectors.
Relevant spectral data is mostly contained within the near and mid infrared regimes. However, Moisture
Content, Carbon, Phosphorous, and pH all have spectral fingerprints that can be detected within the visible
and near infrared spectrum. A reflectance scanning spectrometer with a broadband source and one or two
cheap detectors covering the 400-1700nm range are sufficient to measure these variables\cite{Mouazen2007}.

In addition to professional products and services, hobby project forums are also advancing the
accessibility of complex systems. Hydroponic gardeners are experimenting with water distribution systems,
Arduino programmers have created a market for cheap network communication devices, and optoelectronics
hobbyists have even developed DIY optical spectrometers\cite{Cao}. These projects represent a major development in
engineering activity. It is now possible for a small, poorly funded team of amateurs to create a device
with not only mechanical function, but also wireless control and user interfacing.
\newpage
\section{Project Description}                   % Section 2
At the core, this project is a microcontroller project that anybody with a slight understanding of digital communications could accomplish. Our team in the background of our project will cover the novelties of this project that separates us from any ``Garduino'' project that can be found on numerous blogs. In our Goals and Objectives, we will cover how we will accomplish the novelties as well as the specifics as to why our project is better and more marketable.
\input{project-description/project-bg.tex}      % Section 2.1
\input{project-description/goals.tex}           % Section 2.2
\input{project-description/specifications-requirements.tex}    % Section 2.3 - needs work, expanding requirements, better house of quality
\section{Research}                              % Section 3
Our research covers three core components: previous works, related technology, and part selection. 
\input{research/previous-work.tex}              % Section 3.1
\input{research/technology.tex}                 % Section 3.2
\input{research/part-selection.tex}             % Section 3.3 - add information on pros and cons, some real engineering analysis
\section{Design Constraints}                    % Section 4
In this section we will cover the standards we will be adhering to throughout the development of our project as well as some of the realistic constraints that are imposed on us.
\input{design-constraints/standards.tex}        % Section 4.1 - what standards do we have to adhere to?
\input{design-constraints/realistic-constraints.tex} % Section 4.2-4.9 - what concerns are in the project?
\section{System Hardware and Software Design}   % Section 5 - how each section is going to work
\input{design-details/mcu.tex}                  % Section 5.1 
\input{design-details/power.tex}                % Section 5.2
\input{design-details/sensing.tex}              % Section 5.3
\input{design-details/integration.tex}          % section 5.5
\section{Testing}                               % Section 6 - add sections for individual test plans, and integration test
Incremental unit testing will be used during the development process
to ensure each subsystem fulfills design requirements as described in
Section \ref{sec:specs-and-reqs}. Controller subsystem testing will be performed in
\autoref{sec:controller_subsystem_testing}, power subsystem testing will be
performed in \autoref{sec:power_subsystem_testing}, sensing subsystem testing
will be performed in \autoref{sec:sensing_subsystem_testing}, and web subsystem
testing will be performed in \autoref{sec:web_subsystem_testing}. After
subsystems have fulfilled unit testing requirements, integration testing will
be performed with the criteria defined in \autoref{sec:integration_testing}.
\input{testing/mcu-testing.tex}                 % Section 6.1
\input{testing/power-testing.tex}               % Section 6.2
\input{testing/sensing-testing.tex}             % Section 6.3
\input{testing/integration-testing.tex}         % Section 6.5
\section{Administrative Content}                % Section 7
This next section will detail our plans for designing and implementing the project. We will review the methodologies that our team has decided to use and give a brief overview of when we plan to complete different parts of the project. Because this is a living document with our project, you will notice that some items from our Fall section were not completed as originally planned and have been marked as so and also moved to the Spring section. We decided to leave the items in Fall as well as any real project would so that future projects can plan their time more accurately. 
\input{admin-content/milestones.tex}            % Section 7.1 - refine backlog and move here, create gantt chart
\input{admin-content/finance.tex}               % Section 7.2 - update finances what was budgeted versus what was spent
\section{Future Work}
This section will detail what a team starting from where we left off would do and where they could take this project.
\input{design-details/web.tex}                  % Section 5.4
\input{testing/web.tex}
\clearpage
\pagenumbering{Roman}
\input{references/references.tex}               % References
\end{document}